Fractional Types

### 2019-10-31 fracGC/p.tex
more plan

@@

>>>>

Add eta/epsilon leading to \verb|C3.agda|. This code has a runtime
check like current solutions but is more general allowing non-scoped
ancilla allocation and de-allocation. Show examples.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Comonad}

Comonad to keep track to value in focus

@@

Exploit dependent types to reify proofs in the type system. Type
checking requires (partial) eval. Once we have a proof can we somehow
go back to \verb|C3.agda| and remove the runtime check?

Polymorphic type for ancilla?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Trace?}

Add multiplicative trace, do SAT solver
